Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-09 GNproof.tex
really do have to say it with inner and outer vertices

@@

To check that $V(q) \subseteq [a_r-1, j_m-1]$, there are two cases to consider: when $V(p_r) \subseteq [a_r-1, j_m]$ ($[a_r-1, j_m-1]$ if $l >1$), and when this does not hold. In the first case, non-crossing propagators force $V(q) \subseteq [a_r-1, j_m-1]$.

@@

If $V(p_r) \not \subseteq [a_r-1, j_m]$, then there must be some propagator $p_s \in Q_{l-2}\setminus Q_{l-3}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$. Since $p_r$ is outside $q$ in the $a_r-1$ order, and $q \not\in Q_{l-1}$, $q$ cannot be supported on $I_i(p_s)$. It follows that $I_i(p_s) <_i I_i(p_r)$. Therefore $q$ is inside $p_s$ with respect to $<_{a_s - 1}$ as well.

@@

Now repeat the argument above with $p_s$ in place of $p_r$. Either $V(p_s)  \subseteq [a_s-1, j_m]$, or $V(p_s) \not \subseteq [a_s-1, j_m]$. In the first case, $V(q) \subseteq [a_s-1, j_m-1]$. In the second case, there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_s)$. Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required. This completes the induction step.

>>>>

\begin{dfn}
Let $p = (i, j)$ be a propatagor in $W = (\cP, [n])$. Without loss of generality, impose the $<_i$ ordering on $p$. Then $p$ partitions the vertices of $W$ into three groups: $V(p)$, the vertices of $p$, $V_{in}(p) = [i+2, j-1]$, the vertices (other than $V_p$) that can support propagators in $\cP_{in}$, and $V_{in}(p) = [j+2, i-1]$, the vertices (other than $V_p$) that can support propagators in $\cP_{out}$. \end{dfn}

@@

To check that $V(q) \subseteq [a_r-1, j_m-1]$, there are two cases to consider: when $j_m \in V_{out}(p_r)$ in the $a_r-1$ order, and when $j_m \in V_{in}(p_r)$. Note that for $l>0$, $j_m \not \in V(p_r)$ in the $a_r-1$ order.

@@

If $j_m \in V_{out}(p_r)$ in the $a_r-1$ order, then there must be some propagator $p_s \in Q_{l-2}\setminus Q_{l-3}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$. Since $p_r$ is outside $q$ in the $a_r-1$ order, and $q \not\in Q_{l-1}$, $q$ cannot be supported on $I_i(p_s)$. It follows that $I_i(p_s) <_i I_i(p_r)$. Therefore $q$ is inside $p_s$ with respect to $<_{a_s - 1}$ as well.

@@

Now repeat the argument above with $p_s$ in place of $p_r$. Either $j_m \in V_{out}(p_r)$, and when $j_m \in V_{in}(p_r)$. In the first case, $V(q) \subseteq [a_s-1, j_m-1]$. In the second case, there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_s)$. Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required. This completes the induction step.
